---
title: "Lab 7 Rank Based Tests"
author: "Jill Wirt"
date: "November 14, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This is Jill and I created this repo and markdown document. 

COLLABORATOR (AnnaClaire):

```{r}

library(tidyverse)

kermit <- read_csv("kermit.csv")


kermit_hist <- ggplot(kermit, aes(x = Score.pre)) +
  geom_histogram() +
  facet_wrap(~Gender)

kermit_hist

```

Creator (Jill): doing some rank-based tests

```{r}

# Is there a significant difference in pre-talk Kermit scores for males and females?

# Unpaired: Mann-Whitney U

mwu_kermit <- kermit %>% 
  wilcox.test(Score.pre ~ Gender, data = .) 

mwu_kermit

# there is no significant difference in pre-talk Kermit scores for males and females 

```

Collaborator (AnnaClaire)

Is there a significant difference in Kermit ranks for pre-talk and post-talk scores (ignoring all other variables?)

2 tail test

Null: No

if paired, use wilcoxon sign rank

```{r}

wsr_kermit <- wilcox.test(kermit$Score.pre, kermit$Score.post, paired = TRUE)

wsr_kermit
```


There is no significant difference in Kermit rankings before and after his talk (statistical summary...).

